Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
Some comments here and there

The measurements provided by this dataset, can be used both by researchers and practictioners to validate their ideas. Researchers can use the data to experiment with new quality models, or just validate them in real projects. Practitioners who develop several tools that calculate metrics that already exist in this dataset, can use it to validate if their tools work correctly.

@@

In addition, only one version was analysed per project. Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process. This decision rendered the dataset unusable, for research focused on evolutionary changes of a software project.

@@

This dataset is a source of measurements for a large selection of projects, covering the basic scopes of software design, with metrics covering from program size to object-oriented design. In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the maven repository. In addition, our selection process should be more elastic, allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.

>>>>

The measurements provided by this dataset, can be used both by researchers and practitioners to validate their ideas. Researchers can use the data to experiment with new quality models, or just validate them in real projects. Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.

% gousiosg: A unique selling point is DSLs and people who want to do research with
% DSL embedding can use it I would add something here.

@@

In addition, only one version was analysed per project. Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process. This decision renders the dataset unusable,
for research focused on software evolution.

@@

This dataset is a source of measurements for a large selection of projects, covering the basic scopes of software design, with metrics covering from program size to object-oriented design. In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the Maven repository.
%gousiosg: this is like saying that our current selection process is gtp.
%rephrase
In addition, our selection process should be more elastic, allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.
